Novel Methods for Characterizing Peaks from Direct Injection FT-MS Experiments

### 2020-01-17 peakcharacterization_manuscript.Rmd
describing another way we can evaluate that our peak intensities are better compared to something else

>>>>

### Changes in Variance Across a Large Dataset

For large datasets, we expect that more correct peak intensities will result in better agreement between sample normalized peak intensities within a sample class. 
If incorrect peak intensities are being reported, then we would expect between class to within class variances to be very random, resulting in F-statistics close to 1.
For each matched peak across samples, we kept the peaks present in at least 25% of samples in both classes of sample (disease, non-disease), and calculated the F-statistic for peaks generated using our peak-characterization and those from XCMS.
